\Title

### 2022-10-03 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

% !TEX encoding = UTF-8 Unicode
%!TeX TS-program = pdfLaTeX
%!TeX spellcheck = en-US
%!BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTATIONS
% Pixel world
\newcommand{\presynaddr}{a} % pre address
\newcommand{\postsynaddr}{n} % post address
\newcommand{\numevent}{N_{ev}} % total number of events
\newcommand{\presynaddrspace}{\mathcal{A}} %presynaptic address space
\newcommand{\postsynaddrspace}{\mathcal{B}} %postsynaptic address space
\newcommand{\Npol}{N_\text{p}} % number of polarity
\newcommand{\Nneuron}{N_\text{n}} % number of output neurons in the layer
\newcommand{\arank}{r} % address index
\newcommand{\bias}{b} % bias for the MLR model
\newcommand{\synapse}{\sigma} % synapse
\newcommand{\synapticweight}{w} % synaptic weight
\newcommand{\synapticdelay}{\delta} % synaptic delay
\newcommand{\ranksyn}{s} % synapse index
\newcommand{\Nsyn}{N_{s}} % total number of synapses
\newcommand{\activeweights}{\mathcal{W}} 
\newcommand{\timev}{t} % time
\newcommand{\polev}{p} % polarity
\newcommand{\event}{\epsilon} % event
\newcommand{\eventstream}{\xi} % stream of events
\newcommand{\TS}{S} % time surface
\newcommand{\neuron}{\mathbf{n}} % neuron in the SNN (defined by the spatial position and the channel)
\newcommand{\postneuron}{\mathbf{m}} % post synaptic neuron in the SNN (defined by the spatial position and the kernel)
\newcommand{\channel}{\mathbf{p}} % channel
\newcommand{\layer}{\mathbf{L}} % layer
\newcommand{\ms}{\si{\milli\second}}%
\newcommand{\us}{\si{\micro\second}}%
\newcommand{\timecontext}{T} % time context (cf HOTS) matrice gathering last event times
\newcommand{\current}{I} % post synaptic current
\newcommand{\volt}{u} % membrane potential
\newcommand{\volts}{V} % matrix of membrane potentials
\newcommand{\gain}{\gamma} % homeostatic gain
\newcommand{\simil}{\beta} % similarity value
\newcommand{\Nclass}{N_\text{class}} % number of classes for MLR:
\newcommand{\Nx}{N_\text{X}}
\newcommand{\Ny}{N_\text{Y}}
\newcommand{\Ntime}{N_\text{t}}
\newcommand{\kernel}{K} % convolution kernel
%\newcommand{\kernelind}{\mathbf{k}} % indice of the kernel
\newcommand{\kernelind}{k} % indice of the kernel
\newcommand{\Kx}{K_\text{x}}
\newcommand{\Ky}{K_\text{y}}
\newcommand{\Ktime}{K_\text{t}}
\newcommand{\classiflayer}{\mathbf{C}}
\newcommand{\class}{c} % class k of the MLR
\newcommand{\lrweights}{\theta} % matrix of MLR weights
\newcommand{\lrtrue}{y} % true value of the prediction for MLR
\newcommand{\loss}{J} % cost function for MLR
\newcommand{\softmax}{\sigma}
\newcommand{\actfreq}{f}
\newcommand{\decision}{\hat{y}}
\newcommand{\colorsec}{black}
\newcommand{\colorsubsec}{black}
\newcommand{\speed}{v}
\newcommand{\Nspeed}{N_v}
% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

>>>>

% !TEX encoding = UTF-8 Unicode
%!TeX TS-program = pdfLaTeX
%!TeX spellcheck = en-US
%!BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% public
% https://github.com/SpikeAI/pyTERtorch/tree/main/2022-09-30_BiolCybernetics
% https://www.zotero.org/groups/4776796/fastmotiondetection

% private
% https://framateam.org/spikeai/channels/2022-10_icip-bordeaux
% https://www.overleaf.com/project/630f9044c38e7a3cea81a7b2
% 2022-09-30
% Learning heterogeneous delays in a layer of spiking neurons for fast motion detection
% Corresponding Author: Laurent Perrinet
% Biological Cybernetics
% a7f45f8e-87d6-4a30-ac7f-9f0c94e2592a   |  v.1.0

@@

\newcommand{\DataAvailability}{
This works is made reproducible using the following tools. First the code reproducing all figures is available on~\href{ https://github.com/SpikeAI/pyTERtorch}{GitHub}.

\noindent %The paper is available a an~\href{https://arxiv.org/abs/2205.03635}{arXiv preprint} with links to previous versions ands to the code. 
Find also the associated~\href{https://www.zotero.org/groups/4776796/fastmotiondetection}{zotero group} used to regroup relevant literature on the subject.

% public
% https://github.com/SpikeAI/pyTERtorch/tree/main/2022-09-30_BiolCybernetics
% https://www.zotero.org/groups/4776796/fastmotiondetection

% private
% https://framateam.org/spikeai/channels/2022-10_icip-bordeaux
% https://www.overleaf.com/project/630f9044c38e7a3cea81a7b2

%In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. If the study did not report any data, you might add ``Not applicable'' here. Chen
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTATIONS
% Pixel world
\newcommand{\presynaddr}{a} % pre address
\newcommand{\postsynaddr}{n} % post address
\newcommand{\numevent}{N_{ev}} % total number of events
\newcommand{\presynaddrspace}{\mathcal{A}} %presynaptic address space
\newcommand{\postsynaddrspace}{\mathcal{B}} %postsynaptic address space
\newcommand{\Npol}{N_\text{p}} % number of polarity
\newcommand{\Nneuron}{N_\text{n}} % number of output neurons in the layer
\newcommand{\arank}{r} % address index
\newcommand{\bias}{b} % bias for the MLR model
\newcommand{\synapse}{\sigma} % synapse
\newcommand{\synapticweight}{w} % synaptic weight
\newcommand{\synapticdelay}{\delta} % synaptic delay
\newcommand{\ranksyn}{s} % synapse index
\newcommand{\Nsyn}{N_{s}} % total number of synapses
\newcommand{\activeweights}{\mathcal{W}} 
\newcommand{\timev}{t} % time
\newcommand{\polev}{p} % polarity
\newcommand{\event}{\epsilon} % event
\newcommand{\eventstream}{\xi} % stream of events
\newcommand{\TS}{S} % time surface
\newcommand{\neuron}{\mathbf{n}} % neuron in the SNN (defined by the spatial position and the channel)
\newcommand{\postneuron}{\mathbf{m}} % post synaptic neuron in the SNN (defined by the spatial position and the kernel)
\newcommand{\channel}{\mathbf{p}} % channel
\newcommand{\layer}{\mathbf{L}} % layer
\newcommand{\ms}{\si{\milli\second}}%
\newcommand{\us}{\si{\micro\second}}%
\newcommand{\timecontext}{T} % time context (cf HOTS) matrice gathering last event times
\newcommand{\current}{I} % post synaptic current
\newcommand{\volt}{u} % membrane potential
\newcommand{\volts}{V} % matrix of membrane potentials
\newcommand{\gain}{\gamma} % homeostatic gain
\newcommand{\simil}{\beta} % similarity value
\newcommand{\Nclass}{N_\text{class}} % number of classes for MLR:
\newcommand{\Nx}{N_\text{X}}
\newcommand{\Ny}{N_\text{Y}}
\newcommand{\Ntime}{N_\text{t}}
\newcommand{\kernel}{K} % convolution kernel
%\newcommand{\kernelind}{\mathbf{k}} % indice of the kernel
\newcommand{\kernelind}{k} % indice of the kernel
\newcommand{\Kx}{K_\text{x}}
\newcommand{\Ky}{K_\text{y}}
\newcommand{\Ktime}{K_\text{t}}
\newcommand{\classiflayer}{\mathbf{C}}
\newcommand{\class}{c} % class k of the MLR
\newcommand{\lrweights}{\theta} % matrix of MLR weights
\newcommand{\lrtrue}{y} % true value of the prediction for MLR
\newcommand{\loss}{J} % cost function for MLR
\newcommand{\softmax}{\sigma}
\newcommand{\actfreq}{f}
\newcommand{\decision}{\hat{y}}
\newcommand{\colorsec}{black}
\newcommand{\colorsubsec}{black}
\newcommand{\speed}{v}
\newcommand{\Nspeed}{N_v}
% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
